Scaffolder - Software for Reproducible Genome Scaffolding.

### 2011-03-02 src/article.tex
Proof read results section

The scaffold file takes the form of a list of entries. Each entry corresponds
to a region of sequence inserted from the corresponding FASTA file. The
Scaffolder software processes this list in order, converting each to the
corresponding nucleotide sequences, which are then concatenated to produce
a draft super sequence. Each entry in the scaffold file may have attributes
that define whether a sub-sequence or the reverse complement of the sequence
should be used. The types of attributes available, and an example scaffold file
are outlined below. \pb

>>>>

The scaffold file takes the form of a list of entries. Each entry corresponds
to a region of sequence used in the final scaffold sequence. The Scaffolder
software processes this list in order, converting each entry to the
corresponding nucleotide sequence, all entries are then concatenated to produce
a draft super sequence. Each entry in the scaffold file may have attributes
that define whether a sub-sequence or the reverse complement of the sequence
should be used. The types of attributes available, and an example scaffold file
are outlined below. \pb
